An assessment of photometric redshift PDF performance in the context of LSST

### 2018-09-28 paper/tex/introduction.tex
few more edits, add DESC SRD ref

The unprecedented sample size of LSST galaxies, expected to number several billion for the main cosmological sample, necessitates stringent constraints on photo-$z$ accuracy if systematic errors are not to dominate the statistical errors.
The LSST Science Requirements Document (SRD)\footnote{available at \url{https://docushare.lsstcorp.org/docushare/dsweb/Get/LPM-17}} lists the photometric redshift goals for a magnitude limited sample with $i<25$ as: root-mean-square error with a goal of $\sigma_z<0.02(1+z)$; $3\sigma$ ``catastrophic outlier'' rate below $10\%$; bias below $0.003$\footnote{
Note that at the time the SRD was written, these goals were stated in terms of a photo-$z$ point estimate for each galaxy, as was standard in many previous studies, while in this paper we emphasize the importance of using a full photo-$z$ PDF.}.

The tremendous size of LSST's galaxy catalog will be enabled by its exceptional depth, pushing to fainter magnitudes and deeper imaging and including galaxies of lower luminosity and higher redshift than ever before.
The inclusion of these populations introduce major physical degeneracies, for example the Lyman break/Balmer break degeneracy, that were not present in the populations covered in shallower large area surveys like the Sloan Digital Sky Survey \citep[SDSS,][]{York:00} and the Two Micron All Sky Survey \citep[2MASS,][]{Skrutskie:06}.
In order to meet LSST's demanding error budget, it will be necessary to fully characterize those degeneracies wherein multiple redshift solutions have comparable likelihood.

@@

There are numerous techniques for deriving photo-$z$ PDFs from photometry, yet no one method has yet been established as clearly superior.
Quantitative comparisons of photo-$z$ methods have been made before.
The Photo-$z$ Accuracy And Testing \citep[PHAT,][]{Hildebrandt:10} effort focused on point estimates derived from many photometric bands.  \citet{Rau:2015} introduced a new method for improving redshift PDFs using an ordinal classification algorithm.
DES compared several codes for point estimates \citep{Sanchez:14} and a summary statistic of photo-$z$ interim posteriors for tomographically binned galaxy subsamples \citep{Bonnett:16}.  
This paper is distinguished by its inclusion of metrics of photo-$z$ interim posteriors themselves and consideration of both classic and state-of-the-art photo-$z$ algorithms, comparing the performance of several of the most widely employed codes as well as some that have been developed only recently on the basis of metrics appropriate for a probabilistic data product.
The results presented in this work are
%part of the Data Challenge 1 (DC1)
a major focus of the Photometric Redshift working group of the LSST Dark Energy Science Collaboration (LSST-DESC).
This work is laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}} as one of the critical activities to be completed in preparation for dark energy science analysis on the first year LSST data.
This is the first of multiple papers by the working group, which will grow in sophistication.
In this initial paper we focus on evaluating the performance of photometric redshift codes and their ability to produce accurate PDFs in the presence of representative training sets.
This can be thought of as an initial test under near perfect conditions, before further complexities are added in future papers.
Comparing the relative performance of the codes enables us to evaluate whether each code is using information in an optimal way, and may reveal enhancements in some codes and deficiencies in others, either in the fundamental algorithm, or in specific implementation.

>>>>

The unprecedented sample size of LSST galaxies, expected to number several billion for the main cosmological sample, necessitates stringent constraints on photo-$z$ accuracy if systematic errors are not to dominate the statistical errors.
The LSST Science Requirements Document (SRD)\footnote{available at \url{https://docushare.lsstcorp.org/docushare/dsweb/Get/LPM-17}} lists the photometric redshift goals for a magnitude limited sample with $i<25$ as: root-mean-square error with a goal of $\sigma_z<0.02(1+z)$; $3\sigma$ ``catastrophic outlier'' rate below $10\%$; bias below $0.003$\footnote{
Note that at the time the SRD was written, these goals were stated in terms of a photo-$z$ point estimate for each galaxy, as was standard in many previous studies, while in this paper we emphasize the importance of using a full photo-$z$ PDF.}.  The LSST Dark Energy Science Collaboration (LSST-DESC) developed a separate Science Requirements Document \citep{Mandelbaum:2018}, which forecasts the constraining power of five cosmological probes using somewhat conservative assumptions to define requirements on systematic errors for several measurements.  These include even more stringent requirements on photometric redshift performance than those included in the LSST SRD, though the initial LSST-DESC requirements on tomographic bin populations.  The tremendous size of LSST's galaxy catalog will be enabled by its exceptional depth, pushing to fainter magnitudes and deeper imaging and including galaxies of lower luminosity and higher redshift than ever before.
The inclusion of these populations introduce major physical degeneracies, for example the Lyman break/Balmer break degeneracy, that were not present in the populations covered in shallower large area surveys like the Sloan Digital Sky Survey \citep[SDSS,][]{York:00} and the Two Micron All Sky Survey \citep[2MASS,][]{Skrutskie:06}.
In order to meet the demanding error budgets of LSST and LSST-DESC it will be necessary to fully characterize those degeneracies wherein multiple redshift solutions have comparable likelihood.

@@

There are numerous techniques for deriving photo-$z$ PDFs from photometry, yet no one method has yet been established as clearly superior.
Quantitative comparisons of photo-$z$ methods have been made before.
The Photo-$z$ Accuracy And Testing \citep[PHAT,][]{Hildebrandt:10} effort focused on point estimates derived from many photometric bands.  \citet{Rau:2015} introduced a new method for improving redshift PDFs using an ordinal classification algorithm.
DES compared several codes for point estimates \citep{Sanchez:14} and a summary statistic of photo-$z$ interim posteriors for tomographically binned galaxy subsamples \citep{Bonnett:16}.  
This paper is distinguished by its inclusion of metrics of photo-$z$ interim posteriors themselves and consideration of both classic and state-of-the-art photo-$z$ algorithms, comparing the performance of several of the most widely employed codes as well as some that have been developed only recently on the basis of metrics appropriate for a probabilistic data product.
The results presented in this work are
%part of the Data Challenge 1 (DC1)
a major focus of the Photometric Redshift working group of the LSST-DESC.
This work is laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}} as one of the critical activities to be completed in preparation for dark energy science analysis on the first year LSST data.
This is the first of multiple papers by the working group, which will grow in sophistication.
In this initial paper we focus on evaluating the performance of photometric redshift codes and PDF-based performance metrics in the presence of representative training sets.
Comparing the relative performance of the codes enables us to evaluate whether each code is using information in an optimal way, and may reveal enhancements in some codes and deficiencies in others, either in the fundamental algorithm, or in specific implementation.  We note that these initial tests are a necessary requirement for photo-$z$ codes that will be used in cosmological analyses; however, meeting these requirements is only the first stage in the process of accounting for incomplete training samples, object blending, and other complications that realistic samples will encounter in estimating photometric redshifts.  This can be thought of as an initial test under near perfect conditions before further complexities are added in future papers.
